---
title: "Homework 5"
author: "Alexia Witthaus Viñé"
date: "`r Sys.Date()`"
header-includes:
  - \usepackage{booktabs}
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    toc: false
---

```{r,echo = FALSE, warning = FALSE}
load("Hwk5_workspace.Rdata")
library(modelsummary)
library(kableExtra)
library(fixest)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```


# Summary of the data 

```{r}
graph1
```

Some of the policies leading to the reduction could be on the one had the expansion of Medicaid. Some people who previously had to directly purchase their insurance, are now elegible for Medicaid, which is why they don't purchase their insurance anymore.

```{r}
graph2
```

```{r}
graph4
```

\newpage

# Estimate of the ATE's

## Differences in Averages 
```{r}
kable(ate_1, caption = "Differences in averages") %>% 
  kable_styling(latex_options = "hold_position", position = "center")
```


## Different regressions 



```{r}
models <- list(
  "DiD estimation"     = ate_2,
  "DiD with fixed effects" = ate_3,
  "Staggered DiD"     = ate_4
)

modelsummary(models) %>% 
  kable_styling(latex_options = "hold_position", position = "center")
```



The results don't seem too different from each other. 



```{r}
iplot(ate_3, 
      xlab = 'Time to treatment ( DiD with fixed effects)',
      main = 'Event study')

```






```{r}
iplot(ate_4, 
      xlab = 'Time to treatment (Staggered DiD with fixed effects)',
      main = 'Event study')
```





























